### 2022-05-20 Publish Paper/manuscript_main.tex
Update

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Main Text
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{ACKNOWLEDGMENT} \\ 
I would like to express my special thanks of gratitude to my teacher, Dr.Nguyen Viet Dung (dung.nguyenviet1@hust.edu.vn) who gave me the golden support to do this wonderful project. He gave a chance to use High GPU computing computer for AI Training. Otherwise, he also gave me recommendation on how to implement experiment to make a good conclusion such as what I should focus on, what I need to investigate, which metrics I should consider.  
I would like to express my special thanks of gratitude to my teacher, Dr.Nguyen Viet Dung(dung.nguyenviet1@hust.edu.vn) who gave me the golden support to do this wonderful project. He gave me a chance to use High GPU computing computers for AI Training. Furthermore, he also gave me recommendations on how to implement experiments to make a good conclusion such as what I should focus on, what I need to investigate, and which metrics I should consider.  
\section{Introduction}
%The Need of AI-enabled computer-aided diagnostics
Skin cancer is one of the most common cancers leading to worldwide death. Every day, more than 9500\cite{03358} people in the United States are diagnosed with skin cancer. Otherwise, 3.6\cite{03358} million people are diagnosed with basal cell skin cancer each year. According to the Skin Cancer Foundation, the global incidence of skin cancer continues to increase\cite{11872}. In 2019, it is estimated that 192,310 cases of melanoma will be diagnosed in the United States\cite{11872}. On the other hand, if patients are early diagnosed, the survival rate is correlated with 99\%. However, once the disease progresses beyond the skin, survival is poor\cite{11872}. Moreover, with the increasing incidence of skin cancers, low awareness among a growing population, and a lack of adequate clinical expertise and services, there is a need for effective solution. \newline
%The Need of AI-enabled computer-aided diagnostics in Skin Lesion Clasification
Recently, deep learning particularly, and machine learning in general algorithms have emerged to achieve excellent performance on various tasks, especially in skin disease diagnosis tasks. AI-enabled computer-aided diagnostics (CAD) has solutions in three main categories: Diagnosis, Prognosis, and Medical Treatment. Medical imaging, including ultrasound, computed tomography, magnetic resonance imaging, and X-ray image is used extensively in clinical practice. In Diagnosis, Artificial Intelligence (AI) algorithms are applied for disease detection to save progress execution before these diagnosis results are considered by a doctor. In Prognosis, AI algorithms are used to predict the survival rate of a patient based on his/her history and medical data. In Medical Treatment, AI models are applied to building solutions for a specific disease, medicine revolution is an example. In various studies, AI algorithms have provided various end-to-end solutions in the detection of abnormalities such as breast cancer, brain tumors, lung cancer, esophageal cancer, skin lesions, and foot ulcers across multiple image modalities of medical imaging\cite{11872}. \\
%The Success in AI - especially in CNN - some model based CNN
In order to adapt the increase in skin cancer case, AI algorithms over the last decade has a great performance. Some typical models that can be mentioned are DenseNet\cite{06993}, EfficientNet\cite{04861}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, and NasNet\cite{07012}. Some of these models have been used as a backbone model in other studies that I will discuss more in the Related Work section. \\
In this paper, I will analyze the effect of metadata on classifying skin disease. On the other hand, by analyzing the combination of several backbone models, I will also construct an optimized model that has the ability to classify in a balanced way between classes instead of well identifying the majority of classes.

@@

\[L(\theta, x_n) = -\frac{1}{N}\sum_{c=1}^{C}\sum_{n=1}^{N}y^c_n\log(\hat{y}^c_n)\]

@@

Another interesting point found during the experiment is that MobileNetV2, MobileNetV3 and NasNetMobile have small number of parameters and depth, though have relative good performance. The table 8 illustrates the deeper analyzing of the three models. It's clear that MobileNetV3Large and NasNetMobile are the two best performance model. Nevertheless, MobileNetV3Large has less number of parameters and depth than NasNetMobile according to the table 2.At the end of this experiment, I decide to configure the MobileNetV3Large to construct an optimized model. The result of this experiment is illustrated in table 9.\\

@@

@@

In the MobileNetV3Large experiment, the model architecture is constructed by replacing the layers after the $28^th$ layer from the last layer by the Soft-Attention. The Table 9 demonstrate that, the Soft-Attention and the metadata have a good effect on the model. Otherwise, Adding a dense layer does not increase the model performance. The best MobileNetV3Large model architecture is the combination of MobileNetV3Large replaced from $241^th$ layer to the rest by Soft-Attention layer and the metadata, which peak the model performance of 0.86 accuracy rate. This is an optimized and balanced model, the parameters of model is indicated in Table 10.\\

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Main Text
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textbf{ACKNOWLEDGMENT} \\ 
I would like to express my special thanks of gratitude to my teacher, Dr.Nguyen Viet Dung (dung.nguyenviet1@hust.edu.vn) who gave me the golden support to do this wonderful project. He gave a chance to use High GPU computing computer for AI Training. Otherwise, he also gave me recommendation on how to implement experiment to make a good conclusion such as what I should focus on, what I need to investigate, which metrics I should consider.  
\section{Introduction}
%The Need of AI-enabled computer-aided diagnostics
Skin cancer is one of the most common cancers leading to worldwide death. Every day, more than 9500\cite{03358} people in the United States are diagnosed with skin cancer. Otherwise, 3.6\cite{03358} million people are diagnosed with basal cell skin cancer each year. According to the Skin Cancer Foundation, the global incidence of skin cancer continues to increase\cite{11872}. In 2019, it is estimated that 192,310 cases of melanoma will be diagnosed in the United States\cite{11872}. On the other hand, if patients are early diagnosed, the survival rate is correlated with 99\%. However, once the disease progresses beyond the skin, survival is poor\cite{11872}. Moreover, with the increasing incidence of skin cancers, low awareness among a growing population, and a lack of adequate clinical expertise and services, there is a need for effective solution. \newline
%The Need of AI-enabled computer-aided diagnostics in Skin Lesion Clasification
Recently, deep learning particularly, and machine learning in general algorithms have emerged to achieve excellent performance on various tasks, especially in skin disease diagnosis tasks. AI-enabled computer-aided diagnostics (CAD) has solutions in three main categories: Diagnosis, Prognosis, and Medical Treatment. Medical imaging, including ultrasound, computed tomography, magnetic resonance imaging, and X-ray image is used extensively in clinical practice. In Diagnosis, Artificial Intelligence (AI) algorithms are applied for disease detection to save progress execution before these diagnosis results are considered by a doctor. In Prognosis, AI algorithms are used to predict the survival rate of a patient based on his/her history and medical data. In Medical Treatment, AI models are applied to building solutions for a specific disease, medicine revolution is an example. In various studies, AI algorithms have provided various end-to-end solutions in the detection of abnormalities such as breast cancer, brain tumors, lung cancer, esophageal cancer, skin lesions, and foot ulcers across multiple image modalities of medical imaging\cite{11872}. \\
%The Success in AI - especially in CNN - some model based CNN
In order to adapt the increase in skin cancer case, AI algorithms over the last decade has a great performance. Some typical models that can be mentioned are DenseNet\cite{06993}, EfficientNet\cite{04861}, Inception\cite{00567}, MobileNets\cite{04861}\cite{04381}\cite{02244}, ResNet\cite{03385}\cite{05027}, and NasNet\cite{07012}. Some of these models have been used as a backbone model in other studies that I will discuss more in the Related Work section. \\
In this paper, I will analyze the effect of metadata on classifying skin disease. On the other hand, by analyzing the combination of several backbone models, I will also construct an optimized model that has the ability to classify in a balanced way between classes instead of well identifying the majority of classes.

@@

\[L(\theta, x_n) = -\frac{1}{N}\sum_{c=1}^{C}\sum_{n=1}^{N}W_c\times y^c_n \times \log(\hat{y}^c_n)\]

@@

Another interesting point found during the experiment is that MobileNetV2, MobileNetV3 and NasNetMobile have small number of parameters and depth, though have relative good performance. The table 8 illustrates the deeper analyzing of the three models. It's clear that MobileNetV3Large and NasNetMobile are the two best performance model. Nevertheless, MobileNetV3Large has less number of parameters and depth than NasNetMobile according to the table 2.\\

@@

At the end of this experiment, I decide to configure the MobileNetV3Large to construct an optimized model. The result of this experiment is illustrated in table 9.

@@

In the MobileNetV3Large experiment, the model architecture is constructed by replacing the layers after the $28^{th}$ layer from the last layer by the Soft-Attention. The Table 9 demonstrate that, the Soft-Attention and the metadata have a good effect on the model. Otherwise, Adding a dense layer does not increase the model performance. The best MobileNetV3Large model architecture is the combination of MobileNetV3Large replaced from $241^{th}$ layer to the rest by Soft-Attention layer and the metadata, which peak the model performance of 0.86 accuracy rate. This is an optimized and balanced model, the parameters of model is indicated in Table 10 and Table 11.

@@

	\begin{tabular}{| l | c | c | c |}
		Model & MobileNetV3Large & DenseNet201 & InceptionResnetV2\\
		No. Parameters & \textbf{5.5M} & 20.2M & 55.9M\\
		Depth & \textbf{118} & 402 & 449\\
		Accuracy & 0.86 & 0.89 & 0.90\\
		Time Prediction(s/epochs) & \textbf{116} & 1000 & 3500 \\
\caption{How Performance of MobileNetV3Large be optimized}
\label{table:11}
